---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scihubr

<!-- badges: start -->
<!-- badges: end -->

`{scihubr}` is an unofficial API to [sci-hub.se](https://sci-hub.se/), making it easy to download the papers you need within `R`. The package also offers you a citation.

## Installation

The package is only available from [GitHub](https://github.com/) with:

``` r
if (!require("remotes") install.packages("remotes")
remotes::install_github("netique/scihubr")
```
## Example

If you just want ot read a paper as quick as possible, type:

```{r basic, eval=FALSE, include=TRUE}
scihubr::download_paper("url_or_doi_of_your_favourite_paper")
```


Or, state the path and optional `open = FALSE` meaning you do not want to open the result immediately.

```{r optional, eval=FALSE, include=TRUE}
scihubr::download_paper("url_or_doi_of_your_favourite_paper",
  path = "~/my_favourite_paper.pdf",
  open = FALSE
)
```
